|

### 2021-07-16 03-Chp-Systematic-Review.Rmd
End of day:

(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane20001931]

@@

Full-text screening will also be completed in full by the primary author. A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]

@@

There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018a; @sterne2016] and thus directly evaluating the internal validity of a study. Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]

@@

Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] The motivation for this decision was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).

@@

Patient and

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019d; @wilkinson2018b]

@@

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.

>>>>

(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]

@@

Full-text screening will also be completed in full by the primary author. A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage were recorded. Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]

@@

There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study. Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]

@@

Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold. In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS. In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.

@@

Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).

@@

Patient and public memebers were intended to be involved at this poit

@@

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]

@@

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.

### 2021-07-16 04-Chp-CPRD-Analysis.Rmd
End of day:

@@

@@

```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_p1.jpeg"))
```
<!--------------------------------------------------------------------------->

@@

```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_complete_case.jpeg"))
```
<!----------------------------------------------------------------------------->

@@

@@

```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_control_outcomes.jpeg"))
```
<!----------------------------------------------------------------------------->

@@

```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_unadjusted.jpeg"))
```
<!----------------------------------------------------------------------------->

@@

@@

```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
knitr::include_graphics(file.path("figures/cprd-analysis/fp_cohort_entry.jpeg"))
```
<!----------------------------------------------------------------------------->

@@

In the second sensitivity cohort, removing participants coded as female and aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).

@@

```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_pregnancy.jpeg"))
```
<!----------------------------------------------------------------------------->

@@

```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_sta_type.jpeg"))
```
<!----------------------------------------------------------------------------->

>>>>

<!-- TODO Need to add some information on the generation and use of propensity scores -->

@@

<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->

@@

```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_p1.png"))
```
<!--------------------------------------------------------------------------->

@@

```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_complete_case.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r controlOutcomesText, echo = FALSE, message = FALSE}
```

@@

```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_control_outcomes.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_unadjusted.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r cohortEntry, include=FALSE}
```

@@

```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
knitr::include_graphics(file.path("figures/cprd-analysis/forester_cohort_entry.png"))
```
<!----------------------------------------------------------------------------->

@@

In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).

@@

```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_pregnancy.png"))
```
<!----------------------------------------------------------------------------->

@@

```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","forester_sta_type.png"))
```
<!----------------------------------------------------------------------------->

### 2021-07-16 manuscripts/cprd/manuscript.Rmd
End of day:

Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2,3^, Venexia M Walker^1,2,4^, Neil M Davies^1,2^, Richard M Martin^1,2,3^,  Elizabeth Coulthard^5^, George Davey-Smith^1,2,3^,  Patrick G Kehoe^5,6^ and Yoav Ben-Shlomo^2^

(1)	MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
(2)	Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
(3)	NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
(4)	Department of Surgery, University of Pennsylvania Perelman School of Medicine, Philadelphia, USA
(5)	Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
(6)	Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK

@@

LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048). JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol. The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care. YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust. LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1). JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.

@@

__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease and dementia. As a result, these readily modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia. Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.

__Methods:__ A retrospective cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed. Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).

__Results:__ We analyzed `r totaltext` with a median follow-up of `r fu_ab_text`. We found little evidence that lipid-regulating agents were associated with risk of Alzheimer’s disease  (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`). Evidence for an increased risk of one of the control outcomes, ischemic heart disease (`r ihd_text`), indicated the presence of substantial residual confounding related to vascular factors.

__Conclusion:__ We found little evidence that lipid-regulating agents had any effect on Alzheimer’s disease risk. There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.

@@

* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia. In all cases, the estimated associations were driven by the statin subgroup, which comprised the majority of participants in our cohort.

* However, evidence from the control outcome analyses indicated strong residual confounding by indication, mostly likely related to vascular factors.

@@

Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2019a] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments. In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy. Several existing prospective studies have examined the association of LRA use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.

@@

We performed a cohort study using data from the CPRD. Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data. All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).

An *a priori* protocol for this study was published,[@walker2016a] and amendments to this are recorded in Supplementary Materials 1. This study was reported in line with the RECORD guidelines (Supplementary Table 1).[@nicholls2016record]

@@

In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.[@sterne2009a] All covariates included in the analytic model were also included in the imputation model.[@moons2006using] The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).

@@

@@

A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016a] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used. A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]

@@

Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease. No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams]

@@

However, the findings of our analysis are subject to several limitations. There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contained prescriptions for lipid-regulating agents. Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]

Our study may also be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use. Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses. The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors. Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is not know to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible AD to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of vascular cases in the outcome definition increases. A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual. Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]

@@

<!--------------------------------------------------------------------------->
```{r cprdPrimary, echo = FALSE, fig.cap="Test"}
knitr::include_graphics(here::here("figures","cprd-analysis","fp_p1.jpeg"))
```
<!--------------------------------------------------------------------------->

_Figure 1: Results from the primary analyses of CPRD data, stratified by dementia outcome and drug class. All results were obtained using the fully adjusted model and participant age as the time scale._

>>>>

Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2,3^, Venexia M Walker^1,2,4^, Neil M Davies^1,2^, Richard M Martin^1,2,3^,  Elizabeth Coulthard^5^, George Davey-Smith^1,2,3^,  Patrick G Kehoe^5^ and Yoav Ben-Shlomo^2^

(1)	MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
(2)	Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
(3)	NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
(4)	Department of Surgery, University of Pennsylvania Perelman School of Medicine, Philadelphia, USA
(5)	Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK

@@

LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048). JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol. The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care. YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust. LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1, MC_UU_00011/4). JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care. NMD is supported by a Norwegian Research Council Grant number 295989.

@@

__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia. As a result, these modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia. Here, we test the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.

__Methods:__ A cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed. Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible AD).

__Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` participant-years (median: `r fu_text`). We found little evidence that lipid-regulating agents were associated with risk of AD (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`). Evidence from a number of control outcomes (ischeamic heart disease `r ihd_text`; backpain `r backpain_text` and diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding related to vascular factors.

__Conclusion:__ We found little evidence that lipid-regulating agents were associated with reduced on Alzheimer’s disease risk. There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.

@@

* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia. In all cases, the estimated associations were driven by the statin subgroup, which comprised most participants in our cohort.

* Evidence from the control outcome analyses indicated strong residual confounding by indication, mostly likely related to vascular factors.

@@

Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2020] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments. In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy. Several existing prospective studies have examined the association of LRA use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.

@@

We performed a cohort study using data from the CPRD. Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data. Records pre-dating the 1995 cutoff were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).

An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Supplementary Materials 1. This study was reported in line with the RECORD guidelines (Supplementary Table 1).[@nicholls2016record]

@@

In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.[@sterne2009] All covariates included in the analytic model were also included in the imputation model.[@moons2006using] The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).

@@

<!-- TODO Need a little bit here on comparison with Smeeth -->

@@

A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used. A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]

@@

Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease. No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams2020]

@@

However, the findings of our analysis are subject to several limitations. There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contained prescriptions for lipid-regulating agents. Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]

Our study is likely to be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use. Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses. The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors. Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is not know to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible AD to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of vascular cases in the outcome definition increases. A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual. Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]

@@

<!--------------------------------------------------------------------------->
```{r cprdPrimary, echo = FALSE, fig.cap="Test"}
knitr::include_graphics(here::here("figures","cprd-analysis","forester_p1.png"))
```
<!--------------------------------------------------------------------------->

_Figure 1: Hazard ratios produced by the primary analyses of CPRD data, stratified by dementia outcome and drug class. All results were obtained using the fully adjusted model and participant age as the time scale._
